Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
Naming the two stages "primary" and "secondary" is not very informative. How about "feature extraction" and "similarity learning"?

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example.png}
\caption{Spatial and group organization provided by subject 1.
\vl{It would be good to show the three stages of the human-computer interface:
random initialization,
geometric clustering on screen,
and color clustering.
Besides, the figure is not accessible to readers with
color vision deficiencies at the moment.
The color of the clusters should be reinforced with
geometrical information, \eg{} Voronoi cells.
@data @figure}}
\label{fig:xp2display}
\end{figure}

@@

>>>>

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example.png}
\caption{Spatial and group organization provided by subject 1.
\vl{
Why have you chosen subject 1, who made 14 clusters?
This is an unusually large number, according to the
histogram in Figure 2.
It would be more representative of the population to illustrate this figure
with the data of a subject with the median number of clusters.
It would be good to show the three stages of the human-computer interface:
random initialization,
geometric clustering on screen,
and color clustering.
Besides, the figure is not accessible to readers with
color vision deficiencies at the moment.
The color of the clusters should be reinforced with
geometrical information, \eg{} Voronoi cells.
@data @figure}}
\label{fig:xp2display}
\end{figure}

@@

\vl{Naming the two stages "primary" and "secondary" is not very informative.
How about "feature extraction" and "similarity learning"? @writing}
